\section{Early stage researchers}
\label{esrs}
The 12 ESRs form the core of the network, with the training and partnerships providing a scaffold for the completion of their respective outcomes. These ESRs work with HEP and industry partners throughout the 3 years of their doctoral study.\par
e\par
Shortly after the commencement of the ESR positions, each ESR supervisor completed a Personal Career Development Plan with their ESR. This document details the 

\subsection{Structure of ESR positions}
\label{esr-structure}
Each ESR is enrolled as a doctoral student at a partner university for 3 years. This university is typically also the primary institution of the ESR, though the industry-centred ESR projects 2 and 10 (discussed in Section~\ref{esr-positions}) are carried out with industry partners near to the university of enrollment. Where partner universities require a longer period of study or typically provide extensions to a 3 year study programme, commitments to further enrollment are provided by each partner university where necessary. At the end of the period of doctoral study, each ESR will receive a doctorate in particle physics from their university of enrollment.\par
ESRs\par


Each ESR will undertake a secondment in HEP during their studies, either at another partner university or a partner research institute. This is generally organised to last for 6 months, though this varies from project to project.\par


In addition to their time working in HEP, each ESR will also spend time working in industry, typically as a secondment of 3-4 months (though this is again flexible to the specific programme of each ESR position).

\subsection{Examples of ESR positions}
\label{esr-examples}
The ESR positions of the network are summarised in Table~\ref{esr-positions}. Particular examples are also listed below.
\begin{table}[h!]
    \centering
    \caption{Please write your table caption here}
    \label{esr-positions}       
    \begin{tabular}{llll}
    \hline
    Early-stage researcher & Primary affiliation & HEP secondment & Industry secondment \\\hline
    ESR\#: Name & University & CERN & Ximantis \\
    ESR2: Laura Boggia & IBM France (enrolled at Universit\'e Sorbonne) & CERN & Ximantis \\
    ESR7: Jamie Gooding & TU Dortmund on LHCb & CERN & Ximantis \\
    ESR9: Carlos Cocha & University & CERN & Ximantis \\
    ESR10: Joachim Hansen & University & CERN & Ximantis \\
    --- & --- & --- & --- \\\hline
    \end{tabular}
\end{table}
a